Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 measurements.tex
Getting testbed description

\hline
\ac{Raspi} Model & $I_{idle,avg}$ (A)& $I_{proc,avg}$ (A) & $P_{avg}$ (W) \\
\hline
\hline
    \ac{Raspi} 1 &      0.320        &            0.360    & 0.200\\
\hline
    \ac{Raspi} 2 &      0.216        &            0.285    & 0.345\\
\hline
\end{tabular}
\vspace{0.2cm}
\label{tab:average_power_table}
\end{table}
%
From Table~\ref{tab:average_power_table}, we notice that the power expenditure
for both models is almost the same. Thus, the energy behaviour is mostly
dependent on the goodput trends since the power is just an scaling constant.
%
\subsection{Energy per bit}
With power and goodput measurements, we compute the energy per bit of
the previously mentioned cases as described in \eqref{eq:energy_per_bit}.
The trends of the energy per bit are simply the inverse of the goodput since
both metrics are related by an inverse law.

\subsubsection{Encoding}

>>>>

\hline
\ac{Raspi} Model & $I_{idle,avg}$ (A)& $I_{proc,avg}$ (A) & $P_{avg}$ (W) \\
\hline
\hline
    \ac{Raspi} 1 &      0.320        &            0.360    & 0.200\\
\hline
    \ac{Raspi} 2 &      0.216        &            0.285    & 0.345\\
\hline
\end{tabular}
\vspace{0.2cm}
\label{tab:average_power_table}
\end{table}
%
From Table~\ref{tab:average_power_table}, we notice that the power expenditure
for both models is almost the same. Thus, the energy behaviour is mostly
dependent on the goodput trends since the power is just an scaling constant.
%
\subsection{Energy per bit}
With power and goodput measurements, we compute the energy per bit of
the previously mentioned cases as described in \eqref{eq:energy_per_bit}.
The trends of the energy per bit are simply the inverse of the goodput since
both metrics are related by an inverse law. As made with the goodput, we
separate the results descriptions according to the operation carried by the
\ac{Raspi}: Encoding and decoding. Besides this, we differentiate between
the models in our study. The energy per bit consumption removes the dependency
on the amount of packets helping to normalize the results and indicating
consumption on a fair basis for all the configurations and coding operations
involved in the study.

\subsubsection{Encoding}
Figs.~\ref{fig:enc_ene_rasp1} and \ref{fig:enc_ene_rasp2} show the encoding
energy per bit measurements for the \ac{Raspi} 1 and 2 models, respectively.
